Pure Exploration

### 2017-05-25 Pure Exploration/Pure_Exploration.tex
Add proof of lower bound on FB complexity

>>>>

Given the success of UCB, why not try it for this problem as well?

-\textgreater{} What would be the equivalent algorithm? -\textgreater{}
Audibert et al. (2009) -\textgreater{} Adjustment proposed by Audibert
et al. (2015) -\textgreater{} Choose a linear in t to explore more!
-\textgreater{} Show upper bound -\textgreater{} Give at least the
standard steps of lower bound proof
